Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-15 latex/main.tex
Update the pango x events notebook and table

% This table is generated by the notebook tab_pango_x_events
\begin{table}
\caption{
ARG events associated with Pango X lineages.
Each row corresponds to the oldest node assigned the specified
Pango lineage and the ancestor of all nodes assigned that label
(except XBB, XBB.1 and XM; see STAR methods). [MORE DETAILS]
}
\label{tab:pango_x_lineages}
\begin{footnotesize}
\begin{tabular}{lrrrllrl}
\toprule
\multicolumn{5}{l}{Type I RE event: monophyletic for pango}\\
pango & avt & left & right & left p & right p & samp & nested \\
\midrule
XC & 37 & 26768 & 27390 & \textbf{AY.29} & \textbf{B.1.1.7} & 5 & {} \\
XBR & 22 & 22034 & 22190 & \textbf{BN.3.1} & BQ.1.25 & 1 & {} \\
XA & 16 & 20411 & 21765 & \textbf{B.1.177.18} & \textbf{B.1.1.7} & 39 & {} \\
XS & 11 & 9054 & 10449 & AY.103 & \textbf{BA.1.1} & 17 & {} \\
XL & 8 & 5925 & 8393 & \textbf{BA.1.17.2} & \textbf{BA.2} & 64 & {} \\
XBG & 8 & 22305 & 22917 & \textbf{BA.2.76} & \textbf{BA.5.2} & 25 & {} \\
XBD & 7 & 23020 & 24620 & \textbf{BA.2.75.2} & \textbf{BA.5.2.1} & 30 & {} \\
XQ & 7 & 4322 & 5386 & \textbf{BA.1.1.15} & \textbf{BA.2.9} & 55 & {BA.2:37,
XR:17, XAA:17, XU:1, XAM:21, XAG:6} \\
XBB & 6 & 22332 & 22577 & \textbf{BA.2.10} & BM.1.1.1 & 6452 & {BA.2:1} \\
XM & 6 & 17411 & 21595 & \textbf{BA.1.1} & \textbf{BA.2} & 26 & {BA.2:16,
XAL:3} \\
XBF & 5 & 5184 & 9866 & \textbf{BA.5.2.1} & CJ.1 & 185 & {} \\
XF & 5 & 5387 & 6402 & \textbf{AY.4} & \textbf{BA.1} & 16 & {} \\
XY & 5 & 11538 & 12880 & \textbf{BA.1.1} & \textbf{BA.2} & 23 & {} \\
XG & 4 & 5925 & 6513 & \textbf{BA.1.17} & \textbf{BA.2} & 3 & {} \\
XW & 4 & 2833 & 4321 & \textbf{BA.1.1.15} & \textbf{BA.2} & 32 & {} \\
\midrule
\multicolumn{5}{l}{Type II RE event}\\
alias & avt & left & right & left p & right p & desc & by pango \\
\midrule
Xx & 6 & 24504 & 26060 & \textbf{BA.2} & \textbf{BA.1.17.2} & 253 &
{BA.2:156, XZ:48, XAP:20, XAC:18, XAE:9, XAD:2} \\
XE/XH & 6 & 10448 & 11283 & \textbf{BA.1.17.2} & \textbf{BA.2} & 1156 &
{XE:1116, BA.2:37, XH:2, XAF:1} \\
XBH & 6 & 15452 & 22001 & \textbf{BA.2.1} & BA.2.75.2 & 6 & {BA.2:4, XBH:2} \\
XBM & 6 & 22305 & 22917 & \textbf{BA.2.76} & \textbf{BF.3} & 12 & {XBM:10,
BF.3:2} \\ XAF & 5 & 10199 & 10447 & \textbf{BA.1.1} & \textbf{BA.2} & 36 & {BA.2:35,
XAF:1} \\
XJ & 5 & 13196 & 17410 & \textbf{BA.1.17.2} & \textbf{BA.2} & 85 & {XJ:68,
BA.2:17} \\
\bottomrule
\multicolumn{5}{l}{Events closely derived from RE}\\
pango & alias & path len & time & mutations & samples \\
\midrule
XR & XQ & 3 & 11 & 4 & 17 \\
XU & XQ & 6 & 103 & 4 & 1 \\
XAM & XQ & 6 & 43 & 3 & 21 \\
XAA & XQ & 6 & 33 & 3 & 17 \\
XAG & XQ & 6 & 55 & 4 & 6 \\
XAP & Xx & 4 & 67 & 1 & 20 \\
XZ & Xx & 4 & 48 & 1 & 48 \\
XAE & Xx & 2 & 47 & 7 & 9 \\
XAF & XAF & 5 & 140 & 8 & 1 \\
XAL & XM & 3 & 66 & 2 & 3 \\
\midrule
\multicolumn{5}{l}{Non recombinant}\\
pango & muts & parent & samples & nested \\
\midrule
XP & 1 & \textbf{BA.1.1} & 45 & {} \\
XN & 1 & \textbf{BA.2} & 120 & {BA.2:1} \\
XBQ & 1 & CJ.1 & 14 & {} \\
XBK & 1 & CJ.1 & 7 & {} \\
XBE & 3 & BA.5.2 & 65 & {} \\
XB & 2 & B.1 & 192 & {} \\
XAZ & 3 & \textbf{BA.5} & 133 & {} \\
XAV & 3 & BA.5.1.24 & 13 & {} \\
XAU & 1 & BA.2 & 8 & {} \\
XAS & 1 & BA.4 & 77 & {} \\
XAN & 5 & \textbf{BA.5.1} & 7 & {} \\
XAJ & 11 & \textbf{BA.2.12} & 18 & {} \\
\bottomrule
\end{tabular}
\end{footnotesize}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{figures/recombinant_qc}
\caption{
Classification of ``robust'' and artifactual recombination events.
Scatterplot of recombination events by the net number of supporting loci
for the left parent (x-axis) and for the right parent (y-axis). The shaded
regions highlight artifactual recombination events, which have fewer than four
net supporting loci on one side or both sides of the suggested breakpoint.
Colors indicate the primer scheme used for sequencing. The pie charts show
breakdowns of the recombination events by primer scheme per quadrant.
Recombination events associated with the origins of Pango Xs are labeled.
}
\label{fig:recombinant_qc}
\end{figure}

>>>>

% This table is generated by the notebook tab_pango_x_events
\begin{table}
\caption{
ARG events associated with Pango X lineages.
Each row corresponds to the oldest node assigned the specified
Pango lineage and the ancestor of all nodes assigned that label
(except XBB, XBB.1 and XM; see STAR methods). [MORE DETAILS]
}
\label{tab:pango_x_lineages}
\begin{footnotesize}
\begin{tabular}{lrrrllrl}
\toprule
\multicolumn{5}{l}{Type I RE event: monophyletic for pango}\\
pango & avt & left & right & left p & right p & samp & nested \\
\midrule
XC & 37 & 26768 & 27390 & \textbf{AY.29} & \textbf{B.1.1.7} & 5 & {} \\
XBR & 22 & 22034 & 22190 & \textbf{BN.3.1} & BQ.1.25 & 1 & {} \\
XA & 16 & 20411 & 21765 & \textbf{B.1.177.18} & \textbf{B.1.1.7} & 39 & {} \\
XS & 11 & 9054 & 10449 & AY.103 & \textbf{BA.1.1} & 17 & {} \\
XL & 8 & 5925 & 8393 & \textbf{BA.1.17.2} & \textbf{BA.2} & 64 & {} \\
XBG & 8 & 22305 & 22917 & \textbf{BA.2.76} & \textbf{BA.5.2} & 25 & {} \\
XQ & 7 & 4322 & 5386 & \textbf{BA.1.1.15} & \textbf{BA.2.9} & 55 & {BA.2:37,
XR:17, XAA:17, XU:1, XAM:21, XAG:6} \\
XBD & 7 & 23020 & 24620 & \textbf{BA.2.75.2} & \textbf{BA.5.2.1} & 30 & {} \\
XBH & 6 & 15452 & 22001 & \textbf{BA.2.1} & BA.2.75.2 & 6 & {} \\
XM & 6 & 17411 & 21595 & \textbf{BA.1.1} & \textbf{BA.2} & 26 & {BA.2:16,
XAL:3} \\
XBB & 6 & 22332 & 22577 & \textbf{BA.2.10} & BM.1.1.1 & 6452 & {BA.2:1} \\
XY & 5 & 11538 & 12880 & \textbf{BA.1.1} & \textbf{BA.2} & 23 & {} \\
XF & 5 & 5387 & 6402 & \textbf{AY.4} & \textbf{BA.1} & 16 & {} \\
XBF & 5 & 5184 & 9866 & \textbf{BA.5.2.1} & CJ.1 & 185 & {} \\
XW & 4 & 2833 & 4321 & \textbf{BA.1.1.15} & \textbf{BA.2} & 32 & {} \\
XG & 4 & 5925 & 6513 & \textbf{BA.1.17} & \textbf{BA.2} & 3 & {} \\
\midrule
\multicolumn{5}{l}{Type II RE event}\\
alias & avt & left & right & left p & right p & desc & by pango \\
\midrule
Xx & 6 & 24504 & 26060 & \textbf{BA.2} & \textbf{BA.1.17.2} & 253 & {BA.2:156,
XZ:48, XAP:20, XAC:18, XAE:9, XAD:2} \\
XE/XH & 6 & 10448 & 11283 & \textbf{BA.1.17.2} & \textbf{BA.2} & 1156 &
{XE:1116, BA.2:37, XH:2, XAF:1} \\
XBH & 6 & 15452 & 22001 & \textbf{BA.2.1} & BA.2.75.2 & 6 & {XBH:6} \\
XBM & 6 & 22305 & 22917 & \textbf{BA.2.76} & \textbf{BF.3} & 12 & {XBM:10,
BF.3:2} \\
XAF & 5 & 10199 & 10447 & \textbf{BA.1.1} & \textbf{BA.2} & 36 & {BA.2:35,
XAF:1} \\
XJ & 5 & 13196 & 17410 & \textbf{BA.1.17.2} & \textbf{BA.2} & 85 & {XJ:68,
BA.2:17} \\
\bottomrule
\multicolumn{5}{l}{Events closely derived from RE}\\
pango & alias & path len & time & mutations & samples \\
\midrule
XR & XQ & 3 & 11 & 4 & 17 \\
XU & XQ & 6 & 103 & 13 & 1 \\
XAM & XQ & 6 & 40 & 3 & 21 \\
XAA & XQ & 6 & 33 & 3 & 17 \\
XAG & XQ & 6 & 53 & 4 & 6 \\
XAP & Xx & 4 & 66 & 1 & 20 \\
XZ & Xx & 4 & 48 & 1 & 48 \\
XAE & Xx & 2 & 47 & 7 & 9 \\
XAF & XAF & 5 & 140 & 8 & 1 \\
XAL & XM & 3 & 65 & 2 & 3 \\
\midrule
\multicolumn{5}{l}{Non recombinant}\\
pango & muts & parent & samples & nested \\
\midrule
XP & 1 & \textbf{BA.1.1} & 45 & {} \\
XN & 1 & \textbf{BA.2} & 120 & {BA.2:1} \\
XBQ & 1 & CJ.1 & 14 & {} \\
XBK & 1 & CJ.1 & 7 & {} \\
XBE & 3 & BA.5.2 & 65 & {} \\
XB & 2 & B.1 & 192 & {} \\
XAZ & 3 & \textbf{BA.5} & 133 & {} \\
XAV & 3 & BA.5.1.24 & 13 & {} \\
XAU & 1 & BA.2 & 8 & {} \\
XAS & 1 & BA.4 & 77 & {} \\
XAN & 5 & \textbf{BA.5.1} & 7 & {} \\
XAJ & 11 & \textbf{BA.2.12} & 18 & {} \\
\bottomrule
\end{tabular}
\end{footnotesize}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{recombinant_qc}
\caption{
Classification of ``robust'' and artifactual recombination events.
Scatterplot of recombination events by the net number of supporting loci
for the left parent (x-axis) and for the right parent (y-axis). The shaded
regions highlight artifactual recombination events, which have fewer than four
net supporting loci on one side or both sides of the suggested breakpoint.
Colors indicate the primer scheme used for sequencing. The pie charts show
breakdowns of the recombination events by primer scheme per quadrant.
Recombination events associated with the origins of Pango Xs are labeled.
}
\label{fig:recombinant_qc}
\end{figure}
